Reasoning About a Machine with Local Capabilities

### 2019-03-06 toplas/paper.tex
[TOPLAS] Tone down simplification text

\section{A Capability Machine with Local Capabilities}
\label{sec:capab-mach-with}
In this paper, we work with a formalization of a capability machine with all the characteristics of real capability machines as well as local capabilities much like CHERI's.
Otherwise, it is kept as simple as possible.
It is inspired by both the M-Machine~\citep{Carter:1994:HSF:195473.195579} and CHERI~\citep{Watson2015Cheri}.
To avoid tedious details irrelevant to the focus of this paper, we assume an
infinite address space and unbounded integers (see \sectionname~\ref{sec:discussion} for a discussion of these assumptions).

>>>>

\section{A Capability Machine with Local Capabilities}
\label{sec:capab-mach-with}
In this paper, we work with a formalization of a capability machine with all the characteristics of real capability machines as well as local capabilities much like CHERI's.
Otherwise, it is kept as simple as possible.
It is inspired by both the M-Machine~\citep{Carter:1994:HSF:195473.195579} and CHERI~\citep{Watson2015Cheri}.
For simplicity, we assume an
infinite address space and unbounded integers (see \sectionname~\ref{sec:discussion} for a discussion of these assumptions).
